---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# histogramfunction

<!-- badges: start -->
<!-- badges: end -->

The goal of histogramfunction is to automatically draw a histogram graph for the distribution of a numerical variable in the dataset. This will be particularly useful for quickly drawing the distributions if there are too many numerical variables in the dataset and if you want to see the distribution of each numerical variable individually. 

## Installation

You can install this histogramfunction from [Github](https://github.com/) with:

``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-JiaheZh/Histogramfunction")
```

## Example 1

The first example uses the mtcars dataset and plots the distribution of the mpg variable (miles/gallon). A distribution plot should be created by the end. 

```{r}
library(histogramfunction)
library(datasets)
quick_histogram_function(mtcars, mpg)
```

## Example 2

The second example uses the gapminder dataset, and plots the distribution of life expectancy (in years). 

```{r}
library(gapminder)
quick_histogram_function(gapminder, lifeExp)
```

## Example 3

Please pay attention to the variables you want to plot. The variable has to be a numerical variable. If you put a categorical varibale, it won't work. 

The following example purposefully shows an error: var_x has to be a numerical variable. 

```{r, error=TRUE}
quick_histogram_function(gapminder, country)
```

The country variable of the gapminder dataset is a categorical variable, so an error pops out, and the distribution graph can't be plotted. 
